Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-04-12 docs/00-manuscripts/ieee/ieee-manuscript.tex
update "used features during tuning" part

% Selected percentage of features across plots
Large differences were observed between the numbers of features selected during tuning for the subsequent fitting process.
While for RF least features were selected when Oiartzun was the test set ($n = 2$), most features were used for this plot during model fitting for XGBoost and SVM (\autoref{tab:tune-perc-sel-features}).
Most features were selected during optimization when training without Laukiz2 or Oiartzun and least when Laukiz1 served as the test set.
RF used only two features when Oiartzun served as the test data (0.0028 \% of 7675) while 34 and 230 features were seen as optimal during optimization when Laukiz1 and Laukiz2 were the test data, respectively.
In contrast, XGBoost and SVM used in all cases but Laukiz1 (less than 50 features; test set) more than two-thirds of all available features.

>>>>

% Selected percentage of features across plots
Large differences were observed between the numbers of features selected during tuning for the subsequent fitting process across each learner and plot.
While for RF least features were selected when Luiando or Oiartzun were the test set ($n = 1$), more than 90\% of all features were used for test sets Laukiz and Laukiz2 (\autoref{tab:tune-perc-sel-features}).
Overall, SVM used the least features across all plots among all learners, with 24\% for test set Oiartzun being the highest single ploot value.
Every learner behaved quite differently for each plot and no overall pattern could be observed.
RF and XGBoost used very few features only when Oiartzun was the test set (one and three, respectively) whereas this was the plot for which SVM used most features ($n = 119$).
